Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
The stochastic process can simply be written as
\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
process parameterized by its weights and their standard deviation. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
gives a new policy function for each noise vector \(\xi\).

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

>>>>

\subsection{Noisy Networks}
In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
The stochastic process can simply be written as
\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
process parameterized by its weights and their standard deviation. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
gives a new policy function for each noise vector \(\xi\). Although this means
that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
out that for the loss function it is optimising, there always exsit a deterministic
optimal policy. They show through emipirical analysis, however, that this does not
mean that the policy necessarily disregards the noise and converges to a deterministic
policy.

\subsection{Functional Variational Bayesian Neural Networks}
There are several ways of approximating the posterior distribution of the weights
in a neural network with respect to a prior and a dataset. Typically, a static dataset
\(\D\)
Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):
